---
title: "Grazing  Tradeoff Analysis"
output: html_document
date: "2024-10-23"
---

## Install packages
```{r}
require(Rmisc) # Package for doing data summaries. We'll use its summarySE function later to get means and SEs of various datasets for plotting.
require(sciplot) # The bargraph.CI function in this package makes barplots w/ error bars a breeze!
library(Rmisc)
library(sciplot)
library(plyr)

library(stringr) # for extracting numeric values

require(segmented) # for segmented line fitsß
```

## Import data
```{r}
graz.data <- read.csv("/Users/hollyvm/GoogleSync/StudentWork/AGCamara/Grazing_all_Och_MH_MD - ExptData_v2.csv")
#graz.data<- graz.data[graz.data$OldData!= "Y",]

# From Barbaglia et al:
Barbaglia.data <- read.csv("/Users/hollyvm/GoogleSync/StudentWork/AGCamara/BarbagliaData/OchTradeoffData.csv")
```



## Plotting details
```{r}
# Rainbow of colours for the eight strains (as in Barbaglia et al 2024)
# Colours from: https://github.com/BlakeRMills/MetBrewer - Hokusai 1 + a bit of Hokusai 2
col.a <- rgb(96/255,26/255,16/255)
col.b <- rgb(183/255,51/255,48/255)
col.c <- rgb(234/255,95/255,75/255)
col.d <- rgb(233/255,120/255,47/255)
col.e <- rgb(243/255,186/255,81/255)
col.f <- rgb(120/255,171/255,125/255)
col.g <- rgb(0/255,93/255,148/255)
col.h <- rgb(0/255,56/255,98/255)
col.j <- rgb(64/255, 0/255, 128/255)


# Define the colors
col.a <- rgb(96/255,26/255,16/255)
col.b <- rgb(183/255,51/255,48/255)
col.c <- rgb(234/255,95/255,75/255)
col.d <- rgb(233/255,120/255,47/255)
col.e <- rgb(243/255,186/255,81/255)
col.f <- rgb(120/255,171/255,125/255)
col.g <- rgb(0/255,93/255,148/255)
col.h <- rgb(0/255,56/255,98/255)
col.j <- rgb(64/255, 0/255, 128/255)


# Rainbow of colours with reduced opacity for backgrounds of plots
alpha.bg <- .5
col.a.bg <- rgb(96/255,26/255,16/255,alpha.bg)
col.b.bg <- rgb(183/255,51/255,48/255,alpha.bg)
col.c.bg <- rgb(234/255,95/255,75/255,alpha.bg)
col.d.bg <- rgb(233/255,120/255,47/255,alpha.bg)
col.e.bg <- rgb(243/255,186/255,81/255,alpha.bg)
col.f.bg <- rgb(120/255,171/255,125/255,alpha.bg)
col.g.bg <- rgb(0/255,93/255,148/255,alpha.bg)
col.h.bg <- rgb(0/255,56/255,98/255,alpha.bg)
col.j.bg <- rgb(64/255, 0/255, 128/255, alpha.bg)

# Assembling into a vector of colors
col.strains <- c(col.a,col.b,col.c,col.d,col.e,col.f,col.g,col.h, col.j)
col.strains.bg <- c(col.a.bg,col.b.bg,col.c.bg,col.d.bg,col.e.bg,col.f.bg,col.g.bg,col.h.bg,col.j.bg)

# "Mega" vector alternates saturated and unsaturated, for making barplots that show high and low bacterial treatments side by side
mega.col.strains <- rep(NaN,length(col.strains)*2)
mega.col.strains.white <- rep(NaN,length(col.strains)*2)

for(i in 1:length(col.strains)){
  mega.col.strains[2*(i-1)+1] <- col.strains.bg[i]
  mega.col.strains.white[2*(i-1)+1] <- 'white'
  mega.col.strains[2*i] <- col.strains[i]
  mega.col.strains.white[2*i] <- col.strains[i]
}


# Line types for temperatures
ltys <- c(1,2)

# Shapes for replicates
rep.pchs <- c(1,4,5)

xenic.strains <- c(584,590,1148,1150,1391,1392,1393,2951)
rice.strains <- c('584R','590R','1148R','1150R','1391R',"1392R",'1393R','2951R')

```



## Plot population dynamics

```{r}
# Make a list of all the different prey concentrations
preyconc <- levels(as.factor(graz.data$TargetOchConc))
preyconc

# Dates for plotting
days <- c(1:4)
days

# Select the columns to use for plotting
preycolumns <- c(12:15)+1
head(graz.data[,preycolumns]) # see how this subsets the data to just the prey columns?
predcolumns <- c(17:20)+1
head(graz.data[,predcolumns])


# Set up colors for each prey concentration; using VanGogh3 palette from MetBrewer https://github.com/BlakeRMills/MetBrewer
ltgreen <- rgb(156/255,193/255,132/255)
dkgreen <- rgb(31/255,90/255,37/255)
ctrlcol <- 'gray80'
colfunc <- colorRampPalette(c(ltgreen,dkgreen))
col2use <- colfunc(length(preyconc))
col2use


# Set up line types for different predation treatments
predtreats <- levels(as.factor(graz.data$Pred))
predtreats 
ltys <- c(1:length(predtreats))

# Set up shapes for different replicates
pchs <- c(21:25)
reps <- unique(graz.data$Rep)

# Create a list of unique experiments
strains <- sort(unique(graz.data$Strain))
```

Calculating growth rates

```{r, warning=F}
# Add new columns to our data frame that we will use for prey and predator growth rates and y-intercepts. We'll consider both 48 and 72hr windows for the prey.
graz.data$prey.mu.48 <- NaN
graz.data$prey.yint.48 <- NaN
graz.data$prey.R2.48 <- NaN

graz.data$prey.mu.72 <- NaN
graz.data$prey.yint.72 <- NaN
graz.data$prey.R2.72 <- NaN

graz.data$pred.mu.72 <- NaN
graz.data$pred.yint.72 <- NaN
graz.data$pred.R2.72 <- NaN

# Fit the growth curves line-by-line, using lm()

for( i in 1:dim(graz.data)[1] ){ # for each row in the data table
  if(graz.data[i,]$AssayTemp %in% c(24)){ # excluding 30*C data
  
  if(graz.data[i,]$TargetOchConc!=0){ # Only fit prey if we expect positive densities
  # Fit all prey
  lm1 <- lm(log(t(graz.data[i,preycolumns])+1)~days)
  graz.data$prey.mu.72[i] <- summary(lm1)$coefficients[2,1]
  graz.data$prey.yint.72[i] <- summary(lm1)$coefficients[1,1]
  graz.data$prey.R2.72[i] <- summary(lm1)$r.squared
  
  lm1 <- lm(log(t(graz.data[i,preycolumns[1:3]])+1)~days[1:3])
  graz.data$prey.mu.48[i] <- summary(lm1)$coefficients[2,1]
  graz.data$prey.yint.48[i] <- summary(lm1)$coefficients[1,1]
  graz.data$prey.R2.48[i] <- summary(lm1)$r.squared
  
  }
  
  if( graz.data[i,]$Pred!='Control' ){ # Only fit predators if we expect non-zero densities
  # Fit predator
    if(!is.na(graz.data[i,]$D1PredPop)){
  lm1 <- lm(log(t(graz.data[i,predcolumns]))~days)
  graz.data$pred.mu.72[i] <- summary(lm1)$coefficients[2,1]
  graz.data$pred.yint.72[i] <- summary(lm1)$coefficients[1,1]
  graz.data$pred.R2.72[i] <- summary(lm1)$r.squared
  }}
  }
}


```



Let's look at the differences in our 48 vs 72hr curve fits and check our work by adding our growth curves to our plots of population dynamics. This code creates one set of plots for every *Ochromonas* strain type; for strains for which multiple experiments were run, the data are broken down by experiment.

```{r,fig.height=4*3,fig.width=8}
#par(mar=c(4,5,1,1),mfrow=c(4,2))


for(strainctr in 1:length(strains)){

  #if(rem(strainctr,2)==1){
    par(mar=c(4,5,1,1),mfrow=c(3,2))

 # }

StrainChoice <- strains[strainctr]
AssayLightChoice <- 100
AssayTempChoice <- 24

# Subset the dataframe to the focal Ochromonas strain
dat5 <- graz.data[graz.data$Strain==StrainChoice & graz.data$AssayLight==AssayLightChoice&graz.data$AssayTemp==AssayTempChoice,]
if(strainctr==3){ dat5 <- dat5[dat5$OldData!='Y',]}

for(datectr in 1:length(unique(dat5$D1Date))){
  dat1 <- dat5[dat5$D1Date==unique(dat5$D1Date)[datectr],]



# Create a vector of prey concentrations for this Ochromonas strain
preyconc <- levels(as.factor(dat1$TargetOchConc))

colfunc <- colorRampPalette(c('gray90',col.strains[ceiling(strainctr/2)]))
col2use <- colfunc(length(preyconc))


dat2 <- dat1[dat1$TargetOchConc!=0,]


plot(days,dat2[1,preycolumns]+1,las=1,xlab='Time (days)',ylab='',log='y',ylim=c((min(dat2[,preycolumns]+1,na.rm=T)),(max(dat2[,preycolumns]+1,na.rm=T))),type='n',main=paste('CCMP',StrainChoice, ', ', dat2$D1Date[1]))
mtext('Population size (cells/mL)',side=2,line=4)

for(i in 2:length(preyconc)){
  subdat <- dat2[dat2$TargetOchConc==preyconc[i],]
  for(j in 1:dim(subdat)[1]){
    points(days,subdat[j,preycolumns],col=col2use[i],pch=21,bg=col2use[i])
    if(subdat[j,]$Pred=='Control'){
      # 48hr growth curve
      xcoords <- seq(from = min(days), to = max(days[3]), length.out = 100)
      ycoords <- exp(subdat[j,]$prey.yint.48)*exp(subdat[j,]$prey.mu.48*xcoords)
      lines(xcoords,ycoords,col=col2use[i])
      lines(xcoords,ycoords,col='red')
      
      # 72hr growth curve
      xcoords <- seq(from = min(days), to = max(days), length.out = 100)
      ycoords <- exp(subdat[j,]$prey.yint.72)*exp(subdat[j,]$prey.mu.72*xcoords)
      lines(xcoords,ycoords,col=col2use[i])
      
    }      else{
      # 48hr growth curve
      xcoords <- seq(from = min(days), to = max(days[3]), length.out = 100)
      ycoords <- exp(subdat[j,]$prey.yint.48)*exp(subdat[j,]$prey.mu.48*xcoords)
      lines(xcoords,ycoords,col=col2use[i],lty=2)
      lines(xcoords,ycoords,col='red',lty=2)
      
      # 72hr growth curve
      xcoords <- seq(from = min(days), to = max(days), length.out = 100)
      ycoords <- exp(subdat[j,]$prey.yint.72)*exp(subdat[j,]$prey.mu.72*xcoords)
      lines(xcoords,ycoords,col=col2use[i],lty=2)
    }
  }
}


dat2 <- dat1[dat1$Pred!='Control',]

plot(days,dat2[1,predcolumns],las=1,xlab='Time (days)',ylab='Population size (cells/mL)',log='y',ylim=c((min(dat2[,predcolumns],na.rm=T)),(max(dat2[,predcolumns],na.rm=T))),type='n',main='Predator')
#mtext('Population size (cells/mL)',side=2,line=4)

for(i in 1:length(preyconc)){
  subdat <- dat2[dat2$TargetOchConc==preyconc[i],]
  for(j in 1:dim(subdat)[1]){
    points(days,subdat[j,predcolumns],col=col2use[i],pch=21,bg=col2use[i])
      xcoords <- seq(from = min(days), to = max(days), length.out = 100)
      ycoords <- exp(subdat[j,]$pred.yint.72)*exp(subdat[j,]$pred.mu.72*xcoords)
      lines(xcoords,ycoords,col=col2use[i])
      
  }
}
}
}
```

## Compute grazing rates
Our goal is to use the growth rates of the different organisms to determine the grazing rate. A core part of this is determining differences in prey growth rates between experimental and control wells. We should see that, in the presence of O. marina, our prey grow slower.

The first thing that we need to do is match up our control (predator-free) growth rates with our predator ones.
```{r}

graz.data$Strain.D1Date.TargetOchConc.Rep <- paste(graz.data$Strain,graz.data$D1Date,graz.data$TargetOchConc,graz.data$Rep,sep='.')

graz.data$ctrl.prey.mu.72 <- graz.data[graz.data$Pred=='Control',]$prey.mu.72[match(graz.data$Strain.D1Date.TargetOchConc.Rep,graz.data[graz.data$Pred=='Control',]$Strain.D1Date.TargetOchConc.Rep)] # the "match" function is a really powerful tool for linking data. Here, I'm using the "target prey" variable to make sure I match the correct average growth rates to each row in my data frame.

head(graz.data) # we can inspect the data frame to see if this worked. notice how the growth rates line up?

```

However, because the control data are rather noisy for these experiments, we're also going to use an alternate approach in which we use the *mean growth rates* from the control prey treatments and the *mean growth rates* for the predators. This helps to eliminate the rep-by-rep noise and give more accurate estimates of grazing rates.
```{r}

graz.data$Strain.D1Date.TargetOchConc <- paste(graz.data$Strain,graz.data$D1Date,graz.data$TargetOchConc,sep='.')
ctrl.mu.summ <- summarySE(data=graz.data[graz.data$Pred=='Control',],measurevar='prey.mu.72',groupvars = 'Strain.D1Date.TargetOchConc')


graz.data$ctrl.prey.mu.72.mean <- ctrl.mu.summ$prey.mu.72[match(graz.data$Strain.D1Date.TargetOchConc,ctrl.mu.summ$Strain.D1Date.TargetOchConc)] # the "match" function is a really powerful tool for linking data. Here, I'm using the "target prey" variable to make sure I match the correct average growth rates to each row in my data frame.

head(graz.data) # we can inspect the data frame to see if this worked. notice how the growth rates line up?

```

From here, we can compute our grazing rates as the difference between the control and +predator growth rates.
```{r}
# Rep-by-rep
graz.data$prey.g.72 <- graz.data$ctrl.prey.mu.72-graz.data$prey.mu.72
graz.data$prey.g.72 <- graz.data$ctrl.prey.mu.72-graz.data$prey.mu.72

# Mean
graz.data$prey.g.72.mean <- graz.data$ctrl.prey.mu.72.mean-graz.data$prey.mu.72
graz.data$prey.g.72.mean <- graz.data$ctrl.prey.mu.72.mean-graz.data$prey.mu.72
```

Computing the per-predator ingestion rate is a little trickier. Ask someone to show you the calculus on the whiteboard, but essentially what we are doing is using the growth rates of both predators and prey to compute mean populations of both, and then computing the per-predator ingestion rate from there. This method follows Jeong & Latz (1994) (https://www.int-res.com/articles/meps/106/m106p173.pdf)

```{r}
graz.data$prey.popn.24 <- graz.data$D1OchPop*(exp(graz.data$prey.mu.48)-1)/(graz.data$prey.mu.48) # mean prey population
graz.data[graz.data$TargetOchConc==0,]$prey.popn.24 <- 0
graz.data$pred.popn.24 <- graz.data$D1PredPop*(exp(graz.data$pred.mu.72)-1)/(graz.data$pred.mu.72) # mean predator population
graz.data$prey.i.24 <- graz.data$prey.g.72*graz.data$prey.popn.24/graz.data$pred.popn.24 # ingestion = mean prey * grazing rate / mean predator


graz.data$prey.i.24.mean <- graz.data$prey.g.72.mean*graz.data$prey.popn.24/graz.data$pred.popn.24 # ingestion = mean prey * grazing rate / mean predator

# Finally we'll manually fill in grazing and ingestion rates of 0 for 0 prey treatments.
graz.data[graz.data$TargetOchConc==0&graz.data$Pred!='Control',]$prey.g.72 <- 0
graz.data[graz.data$TargetOchConc==0&graz.data$Pred!='Control',]$prey.i.24 <- 0

graz.data[graz.data$TargetOchConc==0&graz.data$Pred!='Control',]$prey.g.72.mean <- 0
graz.data[graz.data$TargetOchConc==0&graz.data$Pred!='Control',]$prey.i.24.mean <- 0
```

### Ingestion vs population size figures

Let's look at our results! A scatterplot lets us see our results as a function of the mean prey concentration. We can even work on fitting our data with a Holling Type II (saturating) functional response. Here, I'm also choosing to fit a line to the most linear part of the data to estimate the predator's attack rate.

```{r, fig.width=10, fig.height=4}
par(mar=c(2,2.5,1,1),mfrow=c(2,4))

linear.fit.maxima <- c(70000, 50000, 40000, 25000, 155000,90000, 60000, 80000)
saturating.fit.maxima <- c(100000, 100000, 90000, 135000, 155000,250000, 170000, 110000)


attack.ests <- as.data.frame(xenic.strains)
colnames(attack.ests) <-'Strain'
attack.ests$a.linear <- NaN
attack.ests$a.linear.se <- NaN
attack.ests$a.sat <- NaN
attack.ests$a.sat.se <- NaN
attack.ests$h.sat <- NaN
attack.ests$h.sat.se <- NaN


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])
  
  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.popn.24,na.rm=T)), ylim=c(0,max(subdat1$prey.i.24,na.rm=T)),las=1)
  
  # Add labeling
  text(x = 0-.06*max(subdat1$prey.popn.24,na.rm=T), y = max(subdat1$prey.i.24,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)
  if(i == 1){
    legend(x='topright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2)
  }
  
  # Add xenic data
  subdat.x <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.x$prey.popn.24,subdat.x$prey.i.24,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.r$prey.popn.24,subdat.r$prey.i.24, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])
  
  # Add linear model for all data
  subdat1.trim <- subdat1[subdat1$prey.popn.24 < linear.fit.maxima[i],]
  lm1 <- nls(prey.i.24 ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = linear.fit.maxima[i])
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=1.5,col=col.strains[i])
  #abline(lm1)
  
  attack.ests$a.linear[i] <- summary(lm1)$parameters[1]
  attack.ests$a.linear.se[i] <- summary(lm1)$parameters[2]



  # Add saturating model for all data
  subdat1.trim <- subdat1[subdat1$prey.popn.24 < saturating.fit.maxima[i],]
  a.est <- summary(lm(subdat1.trim[1:7,]$prey.i.24~subdat1.trim[1:7,]$prey.popn.24))$coefficients[2,1] # estimate initial slope
  h.est <- 1/50 # estimate handling time

  fit1 <- nls(prey.i.24 ~ a*prey.popn.24/(1+a*h*prey.popn.24),data=subdat1.trim,start = list(a = a.est, h = h.est))
  a.fit <- summary(fit1)$parameters[1,1]
  h.fit <- summary(fit1)$parameters[2,1]

  xcoords <- seq(from = 0, to = max(subdat1.trim$prey.popn.24,na.rm=T),length.out = 100)
  ycoords <- a.fit*xcoords/(1+a.fit*h.fit*xcoords)
  lines(xcoords,ycoords,lwd=2,col='black',lty=2)

  attack.ests$a.sat[i] <- summary(fit1)$parameters[1,1]
  attack.ests$a.sat.se[i] <- summary(fit1)$parameters[1,2]
  attack.ests$h.sat[i] <- summary(fit1)$parameters[2,1]
  attack.ests$h.sat.se[i] <- summary(fit1)$parameters[2,2]
}


```

Fitting linear models with cutoffs

```{r, fig.width=10, fig.height=4}
par(mar=c(2,2.5,1,1),mfrow=c(2,4))

linear.fit.maxima <- c(70000, 50000, 40000, 25000, 155000,90000, 60000, 80000)
linear.fit.maxima.x <- c(150000, 100000, 50000, 25000, 155000,120000, 600000, 120000)
linear.fit.maxima.r <- c(70000, 100000, 40000, 150000, 155000,250000, 200000, 120000)
saturating.fit.maxima <- c(100000, 100000, 90000, 135000, 155000,250000, 170000, 110000)


attack.ests <- as.data.frame(xenic.strains)
colnames(attack.ests) <-'Strain'
attack.ests$a.linear <- NaN
attack.ests$a.linear.se <- NaN
attack.ests$a.x.linear <- NaN
attack.ests$a.x.linear.se <- NaN
attack.ests$a.r.linear <- NaN
attack.ests$a.r.linear.se <- NaN
attack.ests$a.sat <- NaN
attack.ests$a.sat.se <- NaN
attack.ests$h.sat <- NaN
attack.ests$h.sat.se <- NaN


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])
  
  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.popn.24,na.rm=T)), ylim=c(0,max(subdat1$prey.i.24,na.rm=T)),las=1)
  
  # Add labeling
  text(x = 0-.06*max(subdat1$prey.popn.24,na.rm=T), y = max(subdat1$prey.i.24,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)
  if(i == 1){
    legend(x='topright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2)
  }
  
  # Add xenic data
  subdat.x <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.x$prey.popn.24,subdat.x$prey.i.24,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.r$prey.popn.24,subdat.r$prey.i.24, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])
  
  # Add linear model for all data
  subdat1.trim <- subdat1[subdat1$prey.popn.24 < linear.fit.maxima[i],]
  lm1 <- nls(prey.i.24 ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = linear.fit.maxima[i])
  yset <- summary(lm1)$parameters[1] * xset
  #lines(xset,yset,lwd=1.5,col=col.strains[i])
  #abline(lm1)
  
  attack.ests$a.linear[i] <- summary(lm1)$parameters[1]
  attack.ests$a.linear.se[i] <- summary(lm1)$parameters[2]
  
  
  # Add linear model for xenic data
  subdat1.trim <- subdat1[subdat1$Strain==xenic.strains[i] ,]
  subdat1.trim <- subdat1[subdat1$Strain==xenic.strains[i] & subdat1$prey.popn.24 < linear.fit.maxima.x[i],]
  lm1 <- nls(prey.i.24 ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.popn.24,na.rm=T),length.out=100)
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=1.5,col=col.strains[i],lty=2)

  attack.ests$a.x.linear[i] <- summary(lm1)$parameters[1]
  attack.ests$a.x.linear.se[i] <- summary(lm1)$parameters[2]
  
  # Add linear model for rice data
  subdat1.trim <- subdat1[subdat1$Strain==rice.strains[i],]
  subdat1.trim <- subdat1[subdat1$Strain==rice.strains[i] & subdat1$prey.popn.24 < linear.fit.maxima.r[i],]
  lm1 <- nls(prey.i.24 ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.popn.24,na.rm=T))
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=1.5,col=col.strains[i],lty=1)

  attack.ests$a.r.linear[i] <- summary(lm1)$parameters[1]
  attack.ests$a.r.linear.se[i] <- summary(lm1)$parameters[2]



  # Add saturating model for all data
  subdat1.trim <- subdat1[subdat1$prey.popn.24 < saturating.fit.maxima[i],]
  a.est <- summary(lm(subdat1.trim[1:7,]$prey.i.24~subdat1.trim[1:7,]$prey.popn.24))$coefficients[2,1] # estimate initial slope
  h.est <- 1/50 # estimate handling time

  fit1 <- nls(prey.i.24 ~ a*prey.popn.24/(1+a*h*prey.popn.24),data=subdat1.trim,start = list(a = a.est, h = h.est))
  a.fit <- summary(fit1)$parameters[1,1]
  h.fit <- summary(fit1)$parameters[2,1]

  xcoords <- seq(from = 0, to = max(subdat1.trim$prey.popn.24,na.rm=T),length.out = 100)
  ycoords <- a.fit*xcoords/(1+a.fit*h.fit*xcoords)
  #lines(xcoords,ycoords,lwd=2,col='black',lty=2)

  attack.ests$a.sat[i] <- summary(fit1)$parameters[1,1]
  attack.ests$a.sat.se[i] <- summary(fit1)$parameters[1,2]
  attack.ests$h.sat[i] <- summary(fit1)$parameters[2,1]
  attack.ests$h.sat.se[i] <- summary(fit1)$parameters[2,2]
}


```

### Ingestion vs abundance, statistically robust
Adjust with breakpoint analysis to make cutoffs more statistically robust

```{r, fig.width=10, fig.height=4.5,warning=F}
par(mar=c(2,2.5,.7,.5))

rowsperpanel <- 5
colsperpanel <- 5
lay.mat <- matrix(data=NA,nrow=2*rowsperpanel+1,ncol=4*colsperpanel+1)
lay.mat[,1] <- 9
lay.mat[2*rowsperpanel+1,] <- 10
for(i in 1:2){
  for(j in 1:4){
    lay.mat[(1+(i-1)*rowsperpanel):(i*rowsperpanel),(2+(j-1)*colsperpanel):(1+j*colsperpanel)] <- 4*(i-1) + j
  }
}
layout(lay.mat)

# Create a data frame to hold the results
attack.ests <- as.data.frame(xenic.strains)
colnames(attack.ests) <-'Strain'
attack.ests$a.linear <- NaN
attack.ests$a.linear.se <- NaN
attack.ests$a.x.linear <- NaN
attack.ests$a.x.linear.se <- NaN
attack.ests$a.r.linear <- NaN
attack.ests$a.r.linear.se <- NaN
attack.ests$a.sat <- NaN
attack.ests$a.sat.se <- NaN
attack.ests$h.sat <- NaN
attack.ests$h.sat.se <- NaN


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])
  
  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.popn.24,na.rm=T)), ylim=c(0,max(subdat1$prey.i.24,na.rm=T)),las=1)
  
  # Add labeling
  text(x = 0-.06*max(subdat1$prey.popn.24,na.rm=T), y = max(subdat1$prey.i.24,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)
  if(i == 8){
    legend(x='topright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2)
  }
  if(i == 1){
    mtext(expression(paste('Ingestion rate (',italic('Ochromonas'),' · ',italic('O. marina')^-1,' · ',d^-1,')')),side=2,cex=.8,at=-6,line=2.5)
  }
  if(i == 6){
    mtext(expression(paste('Prey availability (',italic('Ochromonas'),' · ',mL^-1, ')')),side=1,line=2.7,cex=.8,at=275000)
  }
  
  # Add xenic data
  subdat.x <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.x$prey.popn.24,subdat.x$prey.i.24,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.r$prey.popn.24,subdat.r$prey.i.24, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])
  
  # Add linear model for all data
  ## Test 3 types of model fits
  lm1 <- lm(prey.i.24 ~ prey.popn.24+0, data=subdat1) # +0 forces y-intercept through 0
  o1 <- segmented(lm1)
  o2 <- segmented(lm1,npsi=2)
  
  ## Select amongst them based on smallest p-value
  seg.pvals <- c(summary(lm1)$coefficients[1,4],summary(o1)$coefficients[1,4],summary(o2)$coefficients[1,4])
  
  if(which(seg.pvals==min(seg.pvals))[1]==1){ # If the standard linear model is the best
    # Plot the best-fit model; skipping here
    # Record the data
    attack.ests$a.linear[i] <- summary(lm1)$coefficients[1,1]
    attack.ests$a.linear.se[i] <- summary(lm1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==2){ # If the 1 breakpoint model is the best
    # Plot the best-fit model; skipping here
    # Record the data
    attack.ests$a.linear[i] <- summary(o1)$coefficients[1,1]
    attack.ests$a.linear.se[i] <- summary(o1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==3){ # If the 2 breakpoint model is the best
    # Plot the best-fit model; skipping here
    # Record the data
    attack.ests$a.linear[i] <- summary(o2)$coefficients[1,1]
    attack.ests$a.linear.se[i] <- summary(o2)$coefficients[1,2]
  }

  # Add linear model for xenic data
  ## Test 3 types of model fits
  lm1 <- lm(prey.i.24 ~ prey.popn.24+0, data=subdat1[subdat1$Strain==xenic.strains[i] ,])
  o1 <- segmented(lm1)
  o2 <- segmented(lm1,npsi=2)
  
  ## Select amongst them based on smallest p-value
  seg.pvals <- c(summary(lm1)$coefficients[1,4],summary(o1)$coefficients[1,4],summary(o2)$coefficients[1,4])
  
  if(which(seg.pvals==min(seg.pvals))[1]==1){ # If the standard linear model is the best
    # Plot the best-fit model
    xcoords <- seq(from = 0, to = max(subdat1[subdat1$Strain==xenic.strains[i],]$prey.popn.24,na.rm=T),length.out=100)
    ycoords <- xcoords*summary(lm1)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2,lty=2,col=col.strains[i])
    # Record the data
    attack.ests$a.x.linear[i] <- summary(lm1)$coefficients[1,1]
    attack.ests$a.x.linear.se[i] <- summary(lm1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==2){ # If the 1 breakpoint model is the best
    # Plot the best-fit model
    plot.segmented(o1,add=TRUE,col=col.strains[i],lty=2,lwd=2)
    # Record the data
    attack.ests$a.x.linear[i] <- summary(o1)$coefficients[1,1]
    attack.ests$a.x.linear.se[i] <- summary(o1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==3){ # If the 2 breakpoint model is the best
    # Plot the best-fit model
    plot.segmented(o2,add=TRUE,col=col.strains[i],lty=2,lwd=2)
    # Record the data
    attack.ests$a.x.linear[i] <- summary(o2)$coefficients[1,1]
    attack.ests$a.x.linear.se[i] <- summary(o2)$coefficients[1,2]
  }
  
  
  # Add linear model for rice data
  ## Test 3 types of model fits
  lm1 <- lm(prey.i.24 ~ prey.popn.24+0, data=subdat1[subdat1$Strain==rice.strains[i] ,])
  o1 <- segmented(lm1)
  if(i == 6){
    o2 <- o1
  } else{
  o2 <- segmented(lm1,npsi=2)}
  
  ## Select amongst them based on smallest p-value
  seg.pvals <- c(summary(lm1)$coefficients[1,4],summary(o1)$coefficients[1,4],summary(o2)$coefficients[1,4])
  
  if(which(seg.pvals==min(seg.pvals))[1]==1){ # If the standard linear model is the best
    # Plot the best-fit model
    xcoords <- seq(from = 0, to = max(subdat1[subdat1$Strain==rice.strains[i],]$prey.popn.24,na.rm=T),length.out=100)
    ycoords <- xcoords*summary(lm1)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2,lty=1,col=col.strains[i])
    # Record the data
    attack.ests$a.r.linear[i] <- summary(lm1)$coefficients[1,1]
    attack.ests$a.r.linear.se[i] <- summary(lm1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==2){ # If the 1 breakpoint model is the best
    # Plot the best-fit model
    plot.segmented(o1,add=TRUE,col=col.strains[i],lty=1,lwd=2)
    # Record the data
    attack.ests$a.r.linear[i] <- summary(o1)$coefficients[1,1]
    attack.ests$a.r.linear.se[i] <- summary(o1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==3){ # If the 2 breakpoint model is the best
    # Plot the best-fit model
    plot.segmented(o2,add=TRUE,col=col.strains[i],lty=1,lwd=2)
    # Record the data
    attack.ests$a.r.linear[i] <- summary(o2)$coefficients[1,1]
    attack.ests$a.r.linear.se[i] <- summary(o2)$coefficients[1,2]
  }
}

```


Including just the first line segment
```{r, fig.width=10, fig.height=4.5,warning=F}
par(mar=c(2,2.5,.7,.5))

rowsperpanel <- 5
colsperpanel <- 5
lay.mat <- matrix(data=NA,nrow=2*rowsperpanel+1,ncol=4*colsperpanel+1)
lay.mat[,1] <- 9
lay.mat[2*rowsperpanel+1,] <- 10
for(i in 1:2){
  for(j in 1:4){
    lay.mat[(1+(i-1)*rowsperpanel):(i*rowsperpanel),(2+(j-1)*colsperpanel):(1+j*colsperpanel)] <- 4*(i-1) + j
  }
}
layout(lay.mat)

# Create a data frame to hold the results
attack.ests <- as.data.frame(xenic.strains)
colnames(attack.ests) <-'Strain'
attack.ests$a.linear <- NaN
attack.ests$a.linear.se <- NaN
attack.ests$a.x.linear <- NaN
attack.ests$a.x.linear.se <- NaN
attack.ests$a.r.linear <- NaN
attack.ests$a.r.linear.se <- NaN
attack.ests$a.sat <- NaN
attack.ests$a.sat.se <- NaN
attack.ests$h.sat <- NaN
attack.ests$h.sat.se <- NaN


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])
  
  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.popn.24,na.rm=T)), ylim=c(0,max(subdat1$prey.i.24,na.rm=T)),las=1)
  
  # Add labeling
  text(x = 0-.06*max(subdat1$prey.popn.24,na.rm=T), y = max(subdat1$prey.i.24,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)
  if(i == 1){
    legend(x='topright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2)
    mtext(expression(paste('Ingestion rate (',italic('Ochromonas'),' · ',italic('O. marina')^-1,' · ',d^-1,')')),side=2,cex=.8,at=-6,line=2.5)
  }
  if(i == 6){
    mtext(expression(paste('Prey availability (',italic('Ochromonas'),' · ',mL^-1, ')')),side=1,line=2.7,cex=.8,at=275000)
  }
  
  # Add xenic data
  subdat.x <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.x$prey.popn.24,subdat.x$prey.i.24,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,]
  points(subdat.r$prey.popn.24,subdat.r$prey.i.24, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])
  
  # Add linear model for all data
  ## Test 3 types of model fits
  lm1 <- lm(prey.i.24 ~ prey.popn.24+0, data=subdat1) # +0 forces y-intercept through 0
  o1 <- segmented(lm1)
  o2 <- segmented(lm1,npsi=2)
  
  ## Select amongst them based on smallest p-value
  seg.pvals <- c(summary(lm1)$coefficients[1,4],summary(o1)$coefficients[1,4],summary(o2)$coefficients[1,4])
  
  if(which(seg.pvals==min(seg.pvals))[1]==1){ # If the standard linear model is the best
    # Plot the best-fit model; skipping here
    # Record the data
    attack.ests$a.linear[i] <- summary(lm1)$coefficients[1,1]
    attack.ests$a.linear.se[i] <- summary(lm1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==2){ # If the 1 breakpoint model is the best
    # Plot the best-fit model; skipping here
    # Record the data
    attack.ests$a.linear[i] <- summary(o1)$coefficients[1,1]
    attack.ests$a.linear.se[i] <- summary(o1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==3){ # If the 2 breakpoint model is the best
    # Plot the best-fit model; skipping here
    # Record the data
    attack.ests$a.linear[i] <- summary(o2)$coefficients[1,1]
    attack.ests$a.linear.se[i] <- summary(o2)$coefficients[1,2]
  }

  # Add linear model for xenic data
  ## Test 3 types of model fits
  lm1 <- lm(prey.i.24 ~ prey.popn.24+0, data=subdat1[subdat1$Strain==xenic.strains[i] ,])
  o1 <- segmented(lm1)
  o2 <- segmented(lm1,npsi=2)
  
  ## Select amongst them based on smallest p-value
  seg.pvals <- c(summary(lm1)$coefficients[1,4],summary(o1)$coefficients[1,4],summary(o2)$coefficients[1,4])
  
  if(which(seg.pvals==min(seg.pvals))[1]==1){ # If the standard linear model is the best
    # Plot the best-fit model
    xcoords <- seq(from = 0, to = max(subdat1[subdat1$Strain==xenic.strains[i],]$prey.popn.24,na.rm=T),length.out=100)
    ycoords <- xcoords*summary(lm1)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2.5,lty=2,col=col.strains[i])
    # Record the data
    attack.ests$a.x.linear[i] <- summary(lm1)$coefficients[1,1]
    attack.ests$a.x.linear.se[i] <- summary(lm1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==2){ # If the 1 breakpoint model is the best
    # Plot the best-fit model
    #plot.segmented(o1,add=TRUE,col=col.strains[i],lty=2,lwd=2)
    xcoords <- seq(from = 0, to = o1$psi[1,2],length.out=100)
    ycoords <- xcoords*summary(o1)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2.5,lty=2,col=col.strains[i])
    # Record the data
    attack.ests$a.x.linear[i] <- summary(o1)$coefficients[1,1]
    attack.ests$a.x.linear.se[i] <- summary(o1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==3){ # If the 2 breakpoint model is the best
    # Plot the best-fit model
    xcoords <- seq(from = 0, to = o2$psi[1,2],length.out=100)
    ycoords <- xcoords*summary(o2)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2.5,lty=2,col=col.strains[i])
    # Record the data
    attack.ests$a.x.linear[i] <- summary(o2)$coefficients[1,1]
    attack.ests$a.x.linear.se[i] <- summary(o2)$coefficients[1,2]
  }
  
  
  # Add linear model for rice data
  ## Test 3 types of model fits
  lm1 <- lm(prey.i.24 ~ prey.popn.24+0, data=subdat1[subdat1$Strain==rice.strains[i] ,])
  o1 <- segmented(lm1)
  if(i == 6){
    o2 <- o1
  } else{
  o2 <- segmented(lm1,npsi=2)}
  
  ## Select amongst them based on smallest p-value
  seg.pvals <- c(summary(lm1)$coefficients[1,4],summary(o1)$coefficients[1,4],summary(o2)$coefficients[1,4])
  
  if(which(seg.pvals==min(seg.pvals))[1]==1){ # If the standard linear model is the best
    # Plot the best-fit model
    xcoords <- seq(from = 0, to = max(subdat1[subdat1$Strain==rice.strains[i],]$prey.popn.24,na.rm=T),length.out=100)
    ycoords <- xcoords*summary(lm1)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2,lty=1,col=col.strains[i])
    # Record the data
    attack.ests$a.r.linear[i] <- summary(lm1)$coefficients[1,1]
    attack.ests$a.r.linear.se[i] <- summary(lm1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==2){ # If the 1 breakpoint model is the best
    # Plot the best-fit model
    #plot.segmented(o1,add=TRUE,col=col.strains[i],lty=2,lwd=2)
    xcoords <- seq(from = 0, to = o1$psi[1,2],length.out=100)
    ycoords <- xcoords*summary(o1)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2,lty=1,col=col.strains[i])
    # Record the data
    attack.ests$a.r.linear[i] <- summary(o1)$coefficients[1,1]
    attack.ests$a.r.linear.se[i] <- summary(o1)$coefficients[1,2]
  }
  if(which(seg.pvals==min(seg.pvals))[1]==3){ # If the 2 breakpoint model is the best
    # Plot the best-fit model
    xcoords <- seq(from = 0, to = o2$psi[1,2],length.out=100)
    ycoords <- xcoords*summary(o2)$coefficients[1,1]
    lines(xcoords,ycoords,lwd=2,lty=1,col=col.strains[i])
    # Record the data
    attack.ests$a.r.linear[i] <- summary(o2)$coefficients[1,1]
    attack.ests$a.r.linear.se[i] <- summary(o2)$coefficients[1,2]
  }
  
}

```



### Barplot of attack rates of O. marina on Ochromonas
```{r, fig.height=4, fig.width=6}
par(mar=c(4,4.2,1,1))
barplot(attack.ests$a.linear*1000,las=1, ylim=c(0,max(attack.ests$a.linear+attack.ests$a.linear.se))*1001,names=xenic.strains,xlab='Strain',ylab=expression(paste(italic('O. marina'),' clearance rate (μL ',d^-1,")")), border="black", col = col.strains.bg)
xcoords <- seq(from = 0.75, to = 9.1, length.out=8)
arrows(xcoords,attack.ests$a.linear*1000-attack.ests$a.linear.se*1000,xcoords, attack.ests$a.linear*1000+attack.ests$a.linear.se*1000, code = 3, angle = 90, length = 0.05, col= 'black')


subdat <- as.data.frame(cbind(attack.ests$Strain,attack.ests$a.r.linear,attack.ests$a.r.linear.se))
colnames(subdat) <- c('Strain','attack','se')
subdat$Bact <- 'R'
subdat2 <- as.data.frame(cbind(attack.ests$Strain,attack.ests$a.x.linear,attack.ests$a.x.linear.se))
colnames(subdat2) <- c('Strain','attack','se')
subdat2$Bact <- 'X'

subdat <- rbind(subdat2,subdat)
subdat <- subdat[order(subdat$Strain),]
barplot(subdat$attack*1000,las=1, ylim=c(0,max(subdat$attack+subdat$se))*1001,xlab='Strain',ylab=expression(paste(italic('O. marina'),' clearance rate (μL · ',d^-1,")")), border=rep(col.strains,each=2),lwd=1, col = mega.col.strains.white,space=c(0.7,.1))
xcoords1 <- seq(from = 1.2, to = 20.8, length.out=8)
xcoords2 <- seq(from = 2.3, to = 21.9, length.out = 8)
xcoords <- sort(c(xcoords1,xcoords2))
arrows(xcoords,subdat$attack*1000-subdat$se*1000,xcoords, subdat$attack*1000+subdat$se*1000, code = 3, angle = 90, length = 0.05, col= 'black')
axis(side=1, at = colMeans(rbind(xcoords1,xcoords2)), labels=xenic.strains, padj=-.5 )
legend(x='topright',inset=c(0,0),legend=c('Low Bacteria','High Bacteria'),pch=22,pt.cex=2,bty='n',pt.bg=c('white', 'gray10'), col=c('gray10','gray10'))


# Adding t-test results
barplot(subdat$attack*1000,las=1, ylim=c(0,max(subdat$attack+subdat$se))*1001,xlab='Strain',ylab=expression(paste(italic('O. marina'),' clearance rate (μL · ',d^-1,")")), border=rep(col.strains,each=2),lwd=1, col = mega.col.strains.white,space=c(0.7,.1))
xcoords1 <- seq(from = 1.2, to = 20.8, length.out=8)
xcoords2 <- seq(from = 2.3, to = 21.9, length.out = 8)
xcoords <- sort(c(xcoords1,xcoords2))
xcoords.mean <- colMeans(rbind(xcoords1,xcoords2))
arrows(xcoords,subdat$attack*1000-subdat$se*1000,xcoords, subdat$attack*1000+subdat$se*1000, code = 3, angle = 90, length = 0.05, col= 'black')
axis(side=1, at = xcoords.mean, labels=xenic.strains, padj=-.5 )
legend(x='topright',inset=c(0,0),legend=c('Low Bacteria','High Bacteria'),pch=22,pt.cex=2,bty='n',pt.bg=c('white', 'gray10'), col=c('gray10','gray10'))

pval.text <- rep('',8)
for(i in 1:length(xenic.strains)){
  subdat2 <- subdat[subdat$Strain==xenic.strains[i],]
  max.se <- max(subdat2$se)
  delta.attack <- max(subdat2$attack) - min(subdat2$attack)
  num.ses <- delta.attack / max.se
  if(num.ses > 3){
    pval.text[i] <- '*'
  }
  if(num.ses > 4){
    pval.text[i] <- '**'
  }
  if(num.ses > 5){
    pval.text[i] <- '***'
  }
}
ycoords <- tapply(subdat$attack*1000,subdat$Strain,FUN='max') + .04
text(xcoords.mean,ycoords,pval.text,cex=.75)

```


## O. marina performance

### relative growth rates
Raw growth rates
```{r, fig.width=10, fig.height=4.5,warning=F}
par(mar=c(2,2.5,.7,.5))

rowsperpanel <- 5
colsperpanel <- 5
lay.mat <- matrix(data=NA,nrow=2*rowsperpanel+1,ncol=4*colsperpanel+1)
lay.mat[,1] <- 9
lay.mat[2*rowsperpanel+1,] <- 10
for(i in 1:2){
  for(j in 1:4){
    lay.mat[(1+(i-1)*rowsperpanel):(i*rowsperpanel),(2+(j-1)*colsperpanel):(1+j*colsperpanel)] <- 4*(i-1) + j
  }
}
layout(lay.mat)


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$TargetOchConc!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])
  
  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.popn.24,na.rm=T)), ylim=c(min(subdat1$pred.mu.72,na.rm=T),max(subdat1$pred.mu.72,na.rm=T)),las=1)
  abline(h=0,lty=2)
  
  # Add xenic data
  subdat.x <- subdat1[subdat1$Strain==xenic.strains[i] ,]
  points(subdat.x$prey.popn.24,subdat.x$pred.mu.72,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- subdat1[subdat1$Strain==rice.strains[i],]
  points(subdat.r$prey.popn.24,subdat.r$pred.mu.72, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])
  
  # Add labeling
  text(x = 0-.06*max(subdat1$prey.popn.24,na.rm=T), y = max(subdat1$pred.mu.72,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)
  if(i == 1){
    legend(x='topright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2)
  }
  if(i == 1){
    mtext(expression(paste(italic('O. marina'),' growth rate (',d^-1,')')),side=2,cex=.8,at=-.6,line=2.5)
  }
  if(i == 6){
    mtext(expression(paste('Prey availability (',italic('Ochromonas'),' · ',mL^-1, ')')),side=1,line=2.7,cex=.8,at=275000)
  }
}


```


Relativized growth rates

```{r}
# First, calculate the mean growth rates of O. marina for each experiment
# Create a unique identifier for each experiment
graz.data$Strain.D1Date <- paste(graz.data$Strain,graz.data$D1Date,sep='.')

# Compute O. marina control (0 prey) growth rates for each experiment
ref.Omarina.growthrates <- summarySE(data=graz.data[graz.data$TargetOchConc==0 & !is.na(graz.data$pred.mu.72),],'pred.mu.72',groupvars='Strain.D1Date')

# Second, map the O. marina control growth rates back to their relevant experiment
graz.data$pred.mu.72.ctrl <- ref.Omarina.growthrates$pred.mu.72[match(graz.data$Strain.D1Date,ref.Omarina.growthrates$Strain.D1Date)]

# Third, compute the relativized growth rates
graz.data$pred.mu.72.rel <- graz.data$pred.mu.72-graz.data$pred.mu.72.ctrl

```

```{r, fig.width=10, fig.height=4.5,warning=F}
par(mar=c(2,2.5,.7,.5))

rowsperpanel <- 5
colsperpanel <- 5
lay.mat <- matrix(data=NA,nrow=2*rowsperpanel+1,ncol=4*colsperpanel+1)
lay.mat[,1] <- 9
lay.mat[2*rowsperpanel+1,] <- 10
for(i in 1:2){
  for(j in 1:4){
    lay.mat[(1+(i-1)*rowsperpanel):(i*rowsperpanel),(2+(j-1)*colsperpanel):(1+j*colsperpanel)] <- 4*(i-1) + j
  }
}
layout(lay.mat)

 growth.ests <- as.data.frame(xenic.strains)
 colnames(growth.ests) <-'Strain'
 growth.ests$a.linear <- NaN
 growth.ests$a.linear.se <- NaN
 growth.ests$a.all.linear <- NaN
 growth.ests$a.all.linear.se <- NaN
 growth.ests$a.x.linear <- NaN
 growth.ests$a.x.linear.se <- NaN
 growth.ests$a.r.linear <- NaN
 growth.ests$a.r.linear.se <- NaN
 growth.ests$a.sat <- NaN
 growth.ests$a.sat.se <- NaN
 growth.ests$h.sat <- NaN
 growth.ests$h.sat.se <- NaN


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$TargetOchConc!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])
  
  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.popn.24,na.rm=T)), ylim=c(min(subdat1$pred.mu.72.rel,na.rm=T),max(subdat1$pred.mu.72.rel,na.rm=T)),las=1)
  abline(h=0,lty=1,col='gray50')
  
  # Add labeling
  if(i %in% c(1,2,5,6,7,8)){
    text(x = 0-.06*max(subdat1$prey.popn.24,na.rm=T), y = max(subdat1$pred.mu.72.rel,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)
    }
  if(i %in% c(3,4)){
    text(x = 1.05*max(subdat1$prey.popn.24,na.rm=T), y = max(subdat1$pred.mu.72.rel,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 2)    
  }
  if(i == 8){
    legend(x='topright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2)
  }
  if(i == 1){
    mtext(expression(paste('Relativized ', italic('O. marina'),' growth rate (',d^-1,')')),side=2,cex=.8,at=-.2,line=2.5)
  }
  if(i == 6){
    mtext(expression(paste('Prey availability (',italic('Ochromonas'),' · ',mL^-1, ')')),side=1,line=2.7,cex=.8,at=275000)
  }
  
  # Add xenic data
  subdat.x <- subdat1[subdat1$Strain==xenic.strains[i] ,]
  points(subdat.x$prey.popn.24,subdat.x$pred.mu.72.rel,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- subdat1[subdat1$Strain==rice.strains[i],]
  points(subdat.r$prey.popn.24,subdat.r$pred.mu.72.rel, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])
  
  # Add linear model for subset of data
  subdat1.trim <- subdat1[subdat1$prey.popn.24 < linear.fit.maxima[i],]
  lm1 <- nls(pred.mu.72.rel ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = linear.fit.maxima[i])
  yset <- summary(lm1)$parameters[1] * xset
  #lines(xset,yset,lwd=1.5,col=col.strains[i])

  growth.ests$a.linear[i] <- summary(lm1)$parameters[1]
  growth.ests$a.linear.se[i] <- summary(lm1)$parameters[2]
  
  
  # Add linear model for all data
  subdat1.trim <- subdat1
  lm1 <- nls(pred.mu.72.rel ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.popn.24,na.rm=T),length.out=100)
  yset <- summary(lm1)$parameters[1] * xset
  #lines(xset,yset,lwd=1.5,col='black',lty=2)

  growth.ests$a.all.linear[i] <- summary(lm1)$parameters[1]
  growth.ests$a.all.linear.se[i] <- summary(lm1)$parameters[2]


  # Add linear model for xenic data
  subdat1.trim <- subdat1[subdat1$Strain==xenic.strains[i],]
  lm1 <- nls(pred.mu.72.rel ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.popn.24,na.rm=T),length.out=100)
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=2.5,col=col.strains[i],lty=2)

  growth.ests$a.x.linear[i] <- summary(lm1)$parameters[1]
  growth.ests$a.x.linear.se[i] <- summary(lm1)$parameters[2]
  
  # Add linear model for rice data
  subdat1.trim <- subdat1[subdat1$Strain==rice.strains[i],]
  lm1 <- nls(pred.mu.72.rel ~ a*prey.popn.24, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.popn.24,na.rm=T))
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=2,col=col.strains[i],lty=1)

  growth.ests$a.r.linear[i] <- summary(lm1)$parameters[1]
  growth.ests$a.r.linear.se[i] <- summary(lm1)$parameters[2]

}


```


### growth vs ingestion

```{r}

graz.data$Strain.numeric <- as.numeric(str_extract_all(graz.data$Strain, "\\d+"))
graz.data$Bact <- 'X'
graz.data[graz.data$Strain%in%c('584R','590R','1148R','1150R','1391R','1392R','1393R','2951R'),]$Bact <- "R"

graz.data$Strain.Bact <- paste(graz.data$Strain.numeric,graz.data$Bact,sep='.')
Barbaglia.data$Strain.Bact <- paste(Barbaglia.data$Strain,Barbaglia.data$Bact.short,sep='.')

# Append information for Ochromonas carbon content in pg C per cell
graz.data$C.perOch <- Barbaglia.data$C.perOch[match(graz.data$Strain.Bact,Barbaglia.data$Strain.Bact)]

# Convert ingestion rate from cells to C, divide by 1000 to get ng per day
graz.data$prey.i.24.C <- graz.data$prey.i.24*graz.data$C.perOch/1000

# Append information for Ochromonas carbon content in pg N per cell
graz.data$N.perOch <- Barbaglia.data$N.perOch[match(graz.data$Strain.Bact,Barbaglia.data$Strain.Bact)]

# Convert ingestion rate from cells to C, divide by 1000 to get ng per day
graz.data$prey.i.24.N <- graz.data$prey.i.24*graz.data$N.perOch/1000
```


```{r, fig.width=10, fig.height=4.5,warning=F}
par(mar=c(2,2.5,.7,.5))

rowsperpanel <- 5
colsperpanel <- 5
lay.mat <- matrix(data=NA,nrow=2*rowsperpanel+1,ncol=4*colsperpanel+1)
lay.mat[,1] <- 9
lay.mat[2*rowsperpanel+1,] <- 10
for(i in 1:2){
  for(j in 1:4){
    lay.mat[(1+(i-1)*rowsperpanel):(i*rowsperpanel),(2+(j-1)*colsperpanel):(1+j*colsperpanel)] <- 4*(i-1) + j
  }
}
layout(lay.mat)


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$TargetOchConc!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])

  
  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.i.24.C,na.rm=T)), ylim=c(min(subdat1$pred.mu.72.rel,na.rm=T),max(subdat1$pred.mu.72.rel,na.rm=T)),las=1)
  abline(h=0,lty=1,col='gray50')
  
  # Add xenic data
  subdat.x <- subdat1[subdat1$Strain==xenic.strains[i] ,]
  points(subdat.x$prey.i.24.C,subdat.x$pred.mu.72.rel,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- subdat1[subdat1$Strain==rice.strains[i],]
  points(subdat.r$prey.i.24.C,subdat.r$pred.mu.72.rel, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])

  # Add linear model for xenic data
  subdat1.trim <- subdat1[subdat1$Strain==xenic.strains[i],]
  lm1 <- nls(pred.mu.72.rel ~ a*prey.i.24.C, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.i.24.C,na.rm=T),length.out=100)
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=2.5,col=col.strains[i],lty=2)

  # Add linear model for rice data
  subdat1.trim <- subdat1[subdat1$Strain==rice.strains[i],]
  lm1 <- nls(pred.mu.72.rel ~ a*prey.i.24.C, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.i.24.C,na.rm=T),length.out=100)
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=2,col=col.strains[i],lty=1)
  
  # Add labeling
  if(i %in% c(1,5:8)){
    text(x = 0-.06*max(subdat1$prey.i.24.C,na.rm=T), y = max(subdat1$pred.mu.72.rel,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)}
  if(i %in% c(2:4)){
    text(x = 1.06*max(subdat1$prey.i.24.C,na.rm=T), y = max(subdat1$pred.mu.72.rel,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 2)    
  }
  if(i == 8){
    legend(x='bottomright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2, lty = c(2,1))
  }
  if(i == 1){
    mtext(expression(paste('Relativized ', italic('O. marina'),' growth rate (',d^-1,')')),side=2,cex=.8,at=-.18,line=2.5)
  }
  if(i == 6){
    mtext(expression(paste('Ingestion rate (ng ',italic('Ochromonas'),' C · ',italic('O. marina')^-1,' · ',d^-1,')')),side=1,line=2.7,cex=.8,at=4.5)
  }

}


```

```{r, fig.width=10, fig.height=4.5,warning=F}
par(mar=c(2,2.5,.7,.5))

rowsperpanel <- 5
colsperpanel <- 5
lay.mat <- matrix(data=NA,nrow=2*rowsperpanel+1,ncol=4*colsperpanel+1)
lay.mat[,1] <- 9
lay.mat[2*rowsperpanel+1,] <- 10
for(i in 1:2){
  for(j in 1:4){
    lay.mat[(1+(i-1)*rowsperpanel):(i*rowsperpanel),(2+(j-1)*colsperpanel):(1+j*colsperpanel)] <- 4*(i-1) + j
  }
}
layout(lay.mat)


for(i in 1:length(xenic.strains)){
  subdat1 <- rbind(graz.data[graz.data$TargetOchConc!='Control'& graz.data$Strain==xenic.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,],graz.data[graz.data$Pred!='Control'& graz.data$Strain==rice.strains[i] & graz.data$OldDat2!='Y' & graz.data$prey.i.24 >= 0,])

  # Make the plot
  plot(1,1,type='n',xlab='',ylab='',xlim=c(0,max(subdat1$prey.i.24.N,na.rm=T)), ylim=c(min(subdat1$pred.mu.72.rel,na.rm=T),max(subdat1$pred.mu.72.rel,na.rm=T)),las=1)
  abline(h=0,lty=1,col='black')
  
  # Add xenic data
  subdat.x <- subdat1[subdat1$Strain==xenic.strains[i] ,]
  points(subdat.x$prey.i.24.N,subdat.x$pred.mu.72.rel,pch=21, cex=1.6, col=col.strains[i], bg='white')# bg= col.strains.bg[i])
  
  # Add rice data
  subdat.r <- subdat1[subdat1$Strain==rice.strains[i],]
  points(subdat.r$prey.i.24.N,subdat.r$pred.mu.72.rel, pch=24, cex=1.2, col = col.strains[i], bg = col.strains[i])

  # Add linear model for xenic data
  subdat1.trim <- subdat1[subdat1$Strain==xenic.strains[i],]
  lm1 <- nls(pred.mu.72.rel ~ a*prey.i.24.N, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.i.24.N,na.rm=T),length.out=100)
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=2.5,col=col.strains[i],lty=2)

  # Add linear model for rice data
  subdat1.trim <- subdat1[subdat1$Strain==rice.strains[i],]
  lm1 <- nls(pred.mu.72.rel ~ a*prey.i.24.N, data=subdat1.trim, start = list(a = 0.001))
  xset <- seq(from = 0, to = max(subdat1.trim$prey.i.24.N,na.rm=T),length.out=100)
  yset <- summary(lm1)$parameters[1] * xset
  lines(xset,yset,lwd=2,col=col.strains[i],lty=1)


  # Add labeling
  if(i %in% c(1,5,6,8)){
    text(x = 0-.06*max(subdat1$prey.i.24.N,na.rm=T), y = max(subdat1$pred.mu.72.rel,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 4)}
  if(i %in% c(2:4,7)){
    text(x = 1.06*max(subdat1$prey.i.24.N,na.rm=T), y = max(subdat1$pred.mu.72.rel,na.rm=T)*0.97, xenic.strains[i], col = col.strains[i],cex=1.3, pos = 2)    
  }
  if(i == 8){
    legend(x='bottomright', inset=c(0.02,0.03), legend=c('Low','High'), pch=c(21,24), col=col.strains[i], pt.bg=c('white',col.strains[i]), bty='y', pt.cex=1.6,1.2, lty = c(2,1))
  }
  if(i == 1){
    mtext(expression(paste('Relativized ', italic('O. marina'),' growth rate (',d^-1,')')),side=2,cex=.8,at=-.18,line=2.5)
  }
  if(i == 6){
    mtext(expression(paste('Ingestion rate (ng ',italic('Ochromonas'),' N · ',italic('O. marina')^-1,' · ',d^-1,')')),side=1,line=2.7,cex=.8,at=.9)
  }

  
}


```




## THE BIG RESULT: testing for correlation between Ochromonas palatability and Barbaglia et al. traits

```{r}
Barbaglia.data$Bact.short <- factor(Barbaglia.data$Bact.short,levels=c('X','R'))


# Useful features:
## C.from.grazing.perCperday = carbon obtained from grazing per Ochromonas carbon per day
## P_I.perC = carbon obtained from photosynthesis per Ochromonas carbon per day

```


Grazing
```{r,fig.height=4,fig.width=4}
#Barbaglia.data$Strain.Bact.Light
par(mar=c(4,4,1,1))

attack.summ <- summarySE(data=Barbaglia.data[Barbaglia.data$Light==100,],'Best.a', groupvars=c('Strain','Bact.short'))
attack.summ$O.marina.a <- attack.ests$a.linear[match(attack.summ$Strain,attack.ests$Strain)]
attack.summ$O.marina.a.bact<-NaN
attack.summ$O.marina.a.bact.se<-NaN
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact <- attack.ests$a.x.linear[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact.se <- attack.ests$a.x.linear.se[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact <- attack.ests$a.r.linear[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact.se <- attack.ests$a.r.linear.se[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]

plot(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,las=1, xlab='Ochromonas attack rate', ylab='O. marina attack rate',type='n',ylim=c(0.3,1.6),xlim=c(0.3e-6,4.7e-6))
arrows(attack.summ$Best.a-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$Best.a+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$Best.a,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,pch=c(24,21)[as.factor(attack.summ$Bact.short)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)

pch.strains <- c(21,22,23,24,25,21,22,23)
cex.strains <- c(1.2,1.2,1.2,1,1,1.2,1.2,1.2)
plot(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,las=1, xlab=expression(paste(italic('Ochromonas'),' clearance rate')), ylab=expression(paste(italic('O. marina'),' clearance rate')),type='n',ylim=c(0.2,1.95),xlim=c(0.3e-6,4.7e-6))
arrows(attack.summ$Best.a-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$Best.a+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$Best.a,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains.white)
points(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)
legend(x='topright',inset=c(0.01,0.01),legend=xenic.strains,pch=pch.strains, cex=.8, pt.cex=cex.strains, col=col.strains, pt.bg=col.strains, title='Strain')
```

Chlorophyll
```{r,fig.height=4,fig.width=4}
par(mar=c(4,4,1,1))

attack.summ <- summarySE(data=Barbaglia.data[Barbaglia.data$Light==100,],'chl.percell', groupvars=c('Strain','Bact.short'))
attack.summ$O.marina.a <- attack.ests$a.linear[match(attack.summ$Strain,attack.ests$Strain)]
attack.summ$O.marina.a.bact<-NaN
attack.summ$O.marina.a.bact.se<-NaN
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact <- attack.ests$a.x.linear[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact.se <- attack.ests$a.x.linear.se[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact <- attack.ests$a.r.linear[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact.se <- attack.ests$a.r.linear.se[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]

pch.strains <- c(21,22,23,24,25,21,22,23)
cex.strains <- c(1.2,1.2,1.2,1,1,1.2,1.2,1.2)
plot(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000,las=1, xlab=expression(paste(italic('Ochromonas'),' chlorophyll per cell')), ylab=expression(paste(italic('O. marina'),' clearance rate')),type='n',ylim=c(0.2,1.8),xlim=c(0.12,0.34))
arrows(attack.summ$chl.percell-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$chl.percell+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$chl.percell,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains.white)
points(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)
legend(x='topright',inset=c(0.01,0.01),legend=xenic.strains,pch=pch.strains, cex=.8, pt.cex=cex.strains, col=col.strains, pt.bg=col.strains, title='Strain')
```

Both together
```{r,fig.height=4,fig.width=8}
par(mar=c(4,4,1,0.5),mfrow=c(1,2))

attack.summ <- summarySE(data=Barbaglia.data[Barbaglia.data$Light==100,],'Best.a', groupvars=c('Strain','Bact.short'))
attack.summ$O.marina.a <- attack.ests$a.linear[match(attack.summ$Strain,attack.ests$Strain)]
attack.summ$O.marina.a.bact<-NaN
attack.summ$O.marina.a.bact.se<-NaN
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact <- attack.ests$a.x.linear[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact.se <- attack.ests$a.x.linear.se[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact <- attack.ests$a.r.linear[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact.se <- attack.ests$a.r.linear.se[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]

pch.strains <- c(21,22,23,24,25,21,22,23)
cex.strains <- c(1.2,1.2,1.2,1,1,1.2,1.2,1.2)
plot(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,las=1, xlab=expression(paste(italic('Ochromonas'),' clearance rate')), ylab=expression(paste(italic('O. marina'),' clearance rate')),type='n',ylim=c(0.2,1.95),xlim=c(0.3e-6,4.7e-6))
arrows(attack.summ$Best.a-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$Best.a+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$Best.a,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains.white)
points(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)
legend(x='topright',inset=c(0.01,0.01),legend=xenic.strains,pch=pch.strains, cex=.8, pt.cex=cex.strains, col=col.strains, pt.bg=col.strains, title='Strain')



par(mar=c(4,2.5,1,2))
attack.summ <- summarySE(data=Barbaglia.data[Barbaglia.data$Light==100,],'chl.percell', groupvars=c('Strain','Bact.short'))
attack.summ$O.marina.a <- attack.ests$a.linear[match(attack.summ$Strain,attack.ests$Strain)]
attack.summ$O.marina.a.bact<-NaN
attack.summ$O.marina.a.bact.se<-NaN
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact <- attack.ests$a.x.linear[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact.se <- attack.ests$a.x.linear.se[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact <- attack.ests$a.r.linear[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact.se <- attack.ests$a.r.linear.se[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]

pch.strains <- c(21,22,23,24,25,21,22,23)
cex.strains <- c(1.2,1.2,1.2,1,1,1.2,1.2,1.2)
plot(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000,las=1, xlab=expression(paste(italic('Ochromonas'),' chlorophyll per cell')), ylab=expression(paste(italic('O. marina'),' clearance rate')),type='n',ylim=c(0.2,1.95)) #,xlim=c(0.12,0.34)
arrows(attack.summ$chl.percell-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$chl.percell+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$chl.percell,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains.white)
points(attack.summ$chl.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)
#legend(x='topright',inset=c(0.01,0.01),legend=xenic.strains,pch=pch.strains, cex=.8, pt.cex=cex.strains, col=col.strains, pt.bg=col.strains, title='Strain')
```
Total carbon yield
```{r,fig.height=4,fig.width=4}
par(mar=c(4,4,1,1))

## C.from.grazing.perCperday = carbon obtained from grazing per Ochromonas carbon per day
## P_I.perC = carbon obtained from photosynthesis per Ochromonas carbon per day

Barbaglia.data$TotC.perC <- Barbaglia.data$C.from.grazing.perCperday + Barbaglia.data$P_I.perC
Barbaglia.data$TotC.percell <- Barbaglia.data$TotC.perC * Barbaglia.data$C.perOch

attack.summ <- summarySE(data=Barbaglia.data[Barbaglia.data$Light==100,],'TotC.percell', groupvars=c('Strain','Bact.short'))
attack.summ$O.marina.a <- attack.ests$a.linear[match(attack.summ$Strain,attack.ests$Strain)]
attack.summ$O.marina.a.bact<-NaN
attack.summ$O.marina.a.bact.se<-NaN
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact <- attack.ests$a.x.linear[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact.se <- attack.ests$a.x.linear.se[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact <- attack.ests$a.r.linear[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact.se <- attack.ests$a.r.linear.se[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]

pch.strains <- c(21,22,23,24,25,21,22,23)
cex.strains <- c(1.2,1.2,1.2,1,1,1.2,1.2,1.2)
plot(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000,las=1, xlab=expression(paste(italic('Ochromonas'),' carbon yield rate')), ylab=expression(paste(italic('O. marina'),' clearance rate')),type='n',ylim=c(0.2,1.95),xlim=c(0,250))
arrows(attack.summ$TotC.percell-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$TotC.percell+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$TotC.percell,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains.white)
points(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)
legend(x='topright',inset=c(0.01,0.01),legend=xenic.strains,pch=pch.strains, cex=.8, pt.cex=cex.strains, col=col.strains, pt.bg=col.strains, title='Strain')
```

Combining this with the attack rate figure


```{r,fig.height=4,fig.width=8}
par(mar=c(4,4,1,0.5),mfrow=c(1,2))

attack.summ <- summarySE(data=Barbaglia.data[Barbaglia.data$Light==100,],'Best.a', groupvars=c('Strain','Bact.short'))
attack.summ$O.marina.a <- attack.ests$a.linear[match(attack.summ$Strain,attack.ests$Strain)]
attack.summ$O.marina.a.bact<-NaN
attack.summ$O.marina.a.bact.se<-NaN
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact <- attack.ests$a.x.linear[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact.se <- attack.ests$a.x.linear.se[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact <- attack.ests$a.r.linear[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact.se <- attack.ests$a.r.linear.se[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]

pch.strains <- c(21,22,23,24,25,21,22,23)
cex.strains <- c(1.2,1.2,1.2,1,1,1.2,1.2,1.2)
plot(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,las=1, xlab=expression(paste(italic('Ochromonas'),' clearance rate')), ylab=expression(paste(italic('O. marina'),' clearance rate')),type='n',ylim=c(0.2,1.95),xlim=c(0.3e-6,4.7e-6))
arrows(attack.summ$Best.a-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$Best.a+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$Best.a,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$Best.a,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains.white)
points(attack.summ$Best.a,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)
legend(x='topright',inset=c(0.01,0.01),legend=xenic.strains,pch=pch.strains, cex=.8, pt.cex=cex.strains, col=col.strains, pt.bg=col.strains, title='Strain')



par(mar=c(4,2.5,1,2))
attack.summ <- summarySE(data=Barbaglia.data[Barbaglia.data$Light==100,],'TotC.percell', groupvars=c('Strain','Bact.short'))
attack.summ$O.marina.a <- attack.ests$a.linear[match(attack.summ$Strain,attack.ests$Strain)]
attack.summ$O.marina.a.bact<-NaN
attack.summ$O.marina.a.bact.se<-NaN
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact <- attack.ests$a.x.linear[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='X',]$O.marina.a.bact.se <- attack.ests$a.x.linear.se[match(attack.summ[attack.summ$Bact.short=='X',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact <- attack.ests$a.r.linear[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]
attack.summ[attack.summ$Bact.short=='R',]$O.marina.a.bact.se <- attack.ests$a.r.linear.se[match(attack.summ[attack.summ$Bact.short=='R',]$Strain,attack.ests$Strain)]

pch.strains <- c(21,22,23,24,25,21,22,23)
cex.strains <- c(1.2,1.2,1.2,1,1,1.2,1.2,1.2)
plot(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000,las=1, xlab=expression(paste(italic('Ochromonas'),' carbon yield rate')), ylab=expression(paste(italic('O. marina'),' clearance rate')),type='n',ylim=c(0.2,1.95),xlim=c(0,240))
arrows(attack.summ$TotC.percell-attack.summ$se,attack.summ$O.marina.a.bact*1000, attack.summ$TotC.percell+attack.summ$se,attack.summ$O.marina.a.bact*1000, code = 3, angle = 90, length = 0.03)
arrows(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000 - attack.summ$O.marina.a.bact.se*1000, attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000 + attack.summ$O.marina.a.bact.se*1000, code = 3, angle = 90, length = 0.03)
for(i in 1:length(strains)){
  subdat <- attack.summ[attack.summ$Strain==strains[i],]
  lines(subdat$TotC.percell,subdat$O.marina.a.bact*1000,lty=2,col='gray50')
}
points(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains.white)
points(attack.summ$TotC.percell,attack.summ$O.marina.a.bact*1000,pch=pch.strains[as.factor(attack.summ$Strain)],cex = cex.strains[as.factor(attack.summ$Strain)], col = col.strains[as.factor(attack.summ$Strain)], bg= mega.col.strains)

```

T-tests
```{r}
# Make a holding table
t.test.results <- as.data.frame(xenic.strains)
colnames(t.test.results) <- "Strain"
t.test.results$Och.graz.tval <- NaN
t.test.results$Och.graz.pval <- NaN
t.test.results$Oxy.graz.numSEs <- NaN

for(i in 1:length(xenic.strains)){ # Working strain by strain
strainchoice <- xenic.strains[i]

# Gina's data: Is there a difference in clearance rate between xenic and rice data?
# Negative t-value for Gina's data means the rice strains had *higher* clearance rates than the xenic ones
gina.subdat <- Barbaglia.data[Barbaglia.data$Light==100 & Barbaglia.data$Strain==strainchoice,]
t.test.results$Och.graz.tval[i] <- t.test(Best.a ~ Bact.short,data=gina.subdat)$statistic
t.test.results$Och.graz.pval[i] <- t.test(Best.a ~ Bact.short,data=gina.subdat)$p.value

}

# AG's data: Is there a difference in clearance rate between xenic and rice data?
# Negative test value means rice strains had *higher* clearance rates
subdat <- as.data.frame(cbind(attack.ests$Strain,attack.ests$a.r.linear,attack.ests$a.r.linear.se))
colnames(subdat) <- c('Strain','attack','se')
subdat$Bact <- 'R'
subdat2 <- as.data.frame(cbind(attack.ests$Strain,attack.ests$a.x.linear,attack.ests$a.x.linear.se))
colnames(subdat2) <- c('Strain','attack','se')
subdat2$Bact <- 'X'

subdat <- rbind(subdat2,subdat)
subdat <- subdat[order(subdat$Strain),]

for(i in 1:length(xenic.strains)){
  subdat2 <- subdat[subdat$Strain==xenic.strains[i],]
  max.se <- max(subdat2$se)
  delta.attack <- subdat2[subdat2$Bact=='X',]$attack - subdat2[subdat2$Bact=='R',]$attack
  t.test.results$Oxy.graz.numSEs[i] <- delta.attack / max.se
}

print(t.test.results)
```








